Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Introduction.tex
Fix Citation that was reverted

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size as
well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best
of our knowledge, the largest system that has been verified using
model checking has only 12 processors, in an era when many observers are
predicting mainstream systems with hundreds of processor cores.
\xxx{citation:
http://www.cs.utah.edu/formal\_verification/pdf/xiaofang\_dissertation.pdf (used
data from their related work must cite)}.

@@

>>>>

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size
as well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best of
our knowledge, the largest system that has been verified using model checking
has only 12 processors~\cite{Chen:2008:VHC:1559300}, in an era when many
observers are predicting mainstream systems with hundreds of processor cores.

@@

\adamc{This might be a good place to include a link to the Coq source code.}
